Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-13 manuscript/manuscript.tex
Added D-delta-grid-search figure: added svg, pdf and in manuscript

>>>>

\begin{figure}
\centering
\includegraphics[width=\linewidth]
    {figures/D-delta-grid-search.pdf}
\caption{
    $D$, $\delta$ space divided in three regions (A, B and C) based on 
    the definitions of $D_\text{linear}$ and $\delta_p$ (see text for more 
    information).
    Light grey points are the non-eligible ($D$, $\delta$) pairs 
    belonging to the region A (with $D < D_\text{linear}$).
    Green points have acceptable numerical error (lower than 0.1\%), 
    while the red ones represent those whose error is greater than the 
    threshold.
    Dark grey points represent those from which we don't have a priori 
    information about their numerical error.}
\label{fig:D-delta-grid-search}
\end{figure}
